\documentclass[usenames,xcolor=dvipsnames]{beamer}
\usecolortheme{orchid}
\usetheme{CambridgeUS}

\title{Hints}
\author{Aleksa Sarai, John Cramb}
\institute{\texttt{SYD0x05}}
\date{March 2015}

\usepackage{hyperref}
\hypersetup{pdfpagemode=FullScreen}

\usepackage{float}
\usepackage{color}
\usepackage{graphics}
\usepackage{ulem}
\usepackage{textcomp}

% Define a nice list environment.
\newenvironment{list**}
	{\begin{list}{\textcolor{blue}{$\ast$}}{\leftmargin=1em \itemindent=0em}}
	{\end{list}}

% Define a nice definition environment.
\newenvironment{definition**}
	{\begin{list}{}{\leftmargin=2.5em \itemindent=0em}}
	{\end{list}}

% Define a nice definition environment.
\setbeamertemplate{enumerate items}[default]
\newenvironment{enumerate**}
	{\begin{enumerate}}
	{\end{enumerate}}

% Redefine \sout<> to allow for beamer magic.
\renewcommand<>{\sout}[1]{
  \alt#2{\beameroriginal{\sout}{#1}}{#1}
}

\begin{document}

% Title page.
\begin{frame}
	\titlepage
\end{frame}

% Hello page.
\begin{frame}
	\frametitle{Getting ready for r00t.}
	\begin{list**}
		\item<2-> Point your \texttt{ssh} to \texttt{[REDACTED]}.
		\item<3-> The user is \texttt{ctf}, and the pasword is \dots
		\item<4-> \texttt{GodLovesKermitSex}
		\item<5-> \dots don't ask. It's a Hackers reference.
	\end{list**}
\end{frame}

\begin{frame}
	\frametitle{Hints for Stage 1.}
	\begin{list**}
		\item<1-> Your goal is to get the magic \texttt{flag\{\dots\}} from \texttt{s3cur3s4f3}. Use that to authenticate with \texttt{w00t} to get to stage 2.
		\item<2-> Pay heed to the debugging information!
		\item<3-> The person who wrote the pin generator got it from stack overflow.
		\item<4-> Each pin digit is generated separately.
		\item<5-> What happens with really big input in a note?
		\item<6-> \texttt{dmesg} gives you the \texttt{eip}.
		\item<7-> Little Endian, motherfuckers.
	\end{list**}
\end{frame}

\begin{frame}
	\frametitle{Hints for Stage 2.}
	\begin{list**}
		\item<1-> Your goal is to get the flag in \texttt{/flag}.
		\item<2-> \texttt{ps aux}. What is \texttt{cron} doing?
		\item<3-> What is the first thing you do when given a random unix binary? Hau 2 help?
		\item<4-> Use the directory permissions, Luke.
		\item<5-> The Sysadmin's Golden Rule: Log verbosely and log often.
		\begin{list**}
			\item<6-> What is wrong (from a "too much information" perspective) with the log output?
		\end{list**}
		\item<7-> The person who wrote this program tried to sanitise symlinks. He didn't succeed.
		\item<8-> There are three types of symlinks. Those who care about the directories around them and those who don't. And the ones that are just wrong. \textbf{tl;dr}: \texttt{symlink(2)} is stupid.
	\end{list**}
\end{frame}

\end{document}
